SIR Model with Testing and Isolation Mechanisms

### 2020-11-10 note/SIR_notes.Rnw

>>>>

**Insights from the R0-contour plots**

1. TTI requires lower testing rate than random testing to achieve $R_0=1$.

2. When random testing regime is applied, $W_S=W_I=W_R$,

(i) in the case of perfect isolation of the reported individuals, $\eta_t=0$, the followings are inferred (see the first few columns of the panel plot); 
 - variations of the $\eta_w$ has a negligible effect on the critical testing.
 - for low $\omega$, $R_0$ increases as $\omega$ increases but saturates. This means that when the reporting process is very very slow, increasing the speed of the reporting causes higher $R_0$. Maybe because more people will move to $I_u$ [?, not very sure here.]

 (ii) in case of the non-perfect isolation (see the last column), when $\eta_w$ increases (more awaiting people follow the isolation rules) faster reporting reduces $R_0$.  
Note that it is sensible to expect that $\partial{R_0}/\partial{\omega}<0$. Here we showed that this can be less true.

3. When TTI regime is applied,
